LIONFISH: an expLoratory Interactive tOol for dyNamic visualization and identiFicatIon multidimenSional mecHanisms

### 2024-09-27 manuscript.tex
refs to citep in places

A first step may look into what variables are important for the cluster solution. The interface provides different capabilities that support variable selection. First, a 2D tour view can be used to understand the sensitivity of the grouping to individual variables, in particular when using the manual tour to remove one variable at a time. This is in particular useful when the starting view was obtained through a projection pursuit guided tour~\cite{CBCH94} that optimized for the separation between the labeled groups~\cite{lckl2005}.

>>>>

A first step may look into what variables are important for the cluster solution. The interface provides different capabilities that support variable selection. First, a 2D tour view can be used to understand the sensitivity of the grouping to individual variables, in particular when using the manual tour to remove one variable at a time. This is in particular useful when the starting view was obtained through a projection pursuit guided tour~\citep{CBCH94} that optimized for the separation between the labeled groups~\citep{lckl2005}.
